Measuring contrast processing in the visual system using SSVEP

### 2024-04-07 review.qmd
Added amblyopia fits

Parkinson's
```{python}
import numpy as np
import matplotlib.pyplot as plt

@@

# Amblyopia parameters would follow a similar structure if they were provided.
# Since they're not detailed in your R code, I'll move on to the autism plot.

@@

plt.subplot(2, 2, 4)  # Fourth plot for Parkinson's
plt.plot(finecontrastsdB, respParkPatients, lw=4, color='red', label='Parkinson\'s patients')
plt.plot(finecontrastsdB, respParkControls, lw=4, color='black', linestyle='--', label='Control participants')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 7, 2))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title("(d) Parkinson's")
plt.legend()
# To save the figure
plt.savefig('clinicalplot.pdf')
```

@@

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-18,36), ylim=c(0,6))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="SSVEP response", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

title(main='(b) Amblyopia',cex.main=2)

>>>>

Parkinson's

Alex - it would be good to add some CRFs from @Afsari2014 to the figure. Is it possible to extract either the fitted parameter values or the raw data for some control flies and some mutants? Whatever you think is most compelling.

```{python}
import numpy as np
import matplotlib.pyplot as plt

@@

amblyparams = np.array([
    [0.39, 37.2, 1.4, 0.22],  # amblyopic eye
    [2.33, 111.69, 1.4, 0.22]   # fellow eye
])

# Calculate responses
respambly = amblyparams[0,0] * ((finecontrasts)**amblyparams[0,2] /
                (amblyparams[0,1] + (finecontrasts)**amblyparams[0,2])) + amblyparams[0,3]

respfellow = amblyparams[1,0] * ((finecontrasts)**amblyparams[1,2] /
                (amblyparams[1,1] + (finecontrasts)**amblyparams[1,2])) + amblyparams[1,3]

plt.figure(figsize=(12, 10))
plt.subplot(2, 2, 2)
plt.plot(finecontrastsdB, respambly, lw=4, color='red', label='Amblyopic eye')
plt.plot(finecontrastsdB, respfellow, lw=4, color='black', linestyle='--', label='Fellow eye')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 2, 0.5))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title('(b) Amblyopia')
plt.legend()

@@

plt.subplot(2, 2, 4)  # Fourth plot for Parkinson's
plt.plot(finecontrastsdB, respParkPatients, lw=4, color='red', label='Parkinson\'s patients')
plt.plot(finecontrastsdB, respParkControls, lw=4, color='black', linestyle='--', label='Control participants')
plt.xticks(ticklocsx, ticklabelsx)
plt.yticks(np.arange(0, 7, 2))
plt.xlabel('Target contrast (%)')
plt.ylabel('SSVEP response')
plt.title("(d) Parkinson's")
plt.legend()
# To save the figure
plt.savefig('Figures/clinicalplot.pdf')
```

@@

# fits to data from Baker et al.. (2015)
amblyparams <- matrix(0,nrow=2,ncol=4)
amblyparams[1,] <- c(0.39,37.2,1.4,0.22)  # amblyopic eye
amblyparams[2,] <- c(2.33,111.69,1.4,0.22)  # good eye

respambly <- amblyparams[1,1] * (finecontrasts^amblyparams[1,3]/(amblyparams[1,2] + finecontrasts^amblyparams[2,3])) + amblyparams[1,4]

respfellow <- amblyparams[2,1] * (finecontrasts^amblyparams[2,3]/(amblyparams[2,2] + finecontrasts^amblyparams[2,3])) + amblyparams[2,4]

ticklocsy <- seq(0,2,0.5)
ticklabelsy <- ticklocsy

par(pty="s")  # make axis square
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(-18,36), ylim=c(0,2))   
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = ticklabelsx, side = 1, at=ticklocsx, line=0.3)     
mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)   
title(ylab="SSVEP response", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
title(main='(b) Amblyopia',cex.main=2)

lines(finecontrastsdB,respambly,lwd=4,col='red')
lines(finecontrastsdB,respfellow,lwd=4,lty=2,col='black')

legend(-18,2,c('Amblyopic eye','Fellow eye'),lwd=4,lty=c(1,2),col=c('red','black'),box.lwd=2)
